Kernel Smoothing And Heat Equation

### 2020-11-10 latex/draft.tex
update latex file
Update notes after the reading class on Nov 10

\begin{itemize}
% 11/03/2020  
\item 11/03/2020. We implemented circular smoother on both fixed bandwidth and adaptive bandwidth scenarios; and did the corresponding simulation. We notice adaptive bandwidth cannot beat the optimal fixed bandwidth. Fixed bandwidth achieve the smallest MSE in our $y=\sin(x)$ setting. 
\begin{verbatim}
           euclidean   circular
Adaptive  0.19821445 0.19821445
logb=-3   1.00313133 1.00313133
logb=-2.4 1.00313133 1.00313133
logb=-1.8 1.00313133 1.00313133
logb=-1.2 0.11346202 0.11227971
logb=-0.6 0.02875581 0.02717735
logb=0    0.08004308 0.08145240
logb=0.6  0.44585526 0.52684029
logb=1.2  0.49326980 0.50454607
logb=1.8  0.50018979 0.50094139
logb=2.4  0.50068896 0.50068896
logb=3    0.50068896 0.50068896
\end{verbatim}

TODOLIST:
  \begin{enumerate}
    \item 
    \item 
  \end{enumerate}

>>>>

\begin{itemize}
% 11/10/2020  
\item 11/10/2020. We implemented circular smoother on both fixed bandwidth and adaptive bandwidth scenarios; and did the corresponding simulation. We noticed for the circular data, the adaptive bandwidth cannot beat the optimal fixed bandwidth. Fixed bandwidth achieve the smallest MSE in our $y=\sin(x)$ setting. We also noticed the circular smoother performs better than Euclidean smoother in the circular data ($y=\sin(x)$). 
\begin{verbatim}
           euclidean   circular
Adaptive  0.19821445 0.19821445
logb=-3   1.00313133 1.00313133
logb=-2.4 1.00313133 1.00313133
logb=-1.8 1.00313133 1.00313133
logb=-1.2 0.11346202 0.11227971
logb=-0.6 0.02875581 0.02717735
logb=0    0.08004308 0.08145240
logb=0.6  0.44585526 0.52684029
logb=1.2  0.49326980 0.50454607
logb=1.8  0.50018979 0.50094139
logb=2.4  0.50068896 0.50068896
logb=3    0.50068896 0.50068896
\end{verbatim}

TODOLIST:
  \begin{enumerate}
    \item Compare MSE at 2 boundaries 
    \item manually do the smoothing for certain points, compare the two bandwidth (adaptive vs fixed); expected MSE and empirical MSE should agree. Two scenarios:
    \begin{enumerate}
    \item manual result doesn't equal to the automatic one, debug the result
    \item manual result equal to the auto one. Seek the reason: Taylor expansion is not good enough, higher order term is needed (More observation, smaller bandwidth, smaller window)
    \end{enumerate}
    \item Future: explore the inhomogeneous heat equation (adaptive $\lambda(x)$) 
    $$\frac{\partial f(x,t)}{\partial t}  = \Delta f = \frac{\partial f}{\partial x}[\lambda(x)\frac{\partial f}{\partial x}] \neq  \lambda(x)\frac{\partial^2 f}{
    \partial x^2} $$

    Google the connection between adaptive smoothing and inhomogeneous heat equation 
  \end{enumerate}
